Comparison of the solution of the shallow equation with experimental

### 2015-03-09 doc/paper/paper.tex
Changes in part DamBreak

In all cases below, boundary conditions are all set to reflection wall. 
\section{Dam Break}\label{Sec:Zero}
The initial condition for this and the following cases is given by
\eqm
h_0(x,y)=& 
\begin{cases}
0.25 & x<5.9 \\
0.02 & \text{else}
\end{cases}\\
u_0(x,y) =& 0
\enm

Figure \ref{fig:waveheight_nocolumn} shows the time history of the wave height measured at the center location where the column will be mounted. 
Result from geoclaw agree quite well in general. At around t=3.8, geoclaw accurately predicted the arrival of the shock. 
As for the peak value of this shock, geoclaw overestimated it a little, while OpenFOAM, another open source computational fluid dynamics software gave a better value by solving the Navier-Stokes equations with turbulent model.
After a longer time, the wave gets reflected at the right wall of the tank, which can be seen by the second jump in wave height in the figure. 
Geoclaw also predicted the arrival time of this peak quite well and got only a little overestimation of the peak value.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_nocolumn}
    \caption{time history of wave height for case without a column}
    \label{fig:waveheight_nocolumn}
\end{figure}

Figure \ref{fig:velocityU_nocolumn} gives the time history of the streamwise velocity $u$ from geoclaw and experiment. 
Note that this velocity $u$ in both geoclaw and experiment are depth-averaged. 
Geoclaw accurately predicted the time of the velocity peak as well as the value of the peak. 
After the peak arrived, geoclaw overestimated the value of velocity.
The reason why geoclaw gives a higher velocity may be attributed to its depth-averaged property: water at all depth are propagating with the same speed. In the experiment, the velocity gets smaller as it comes closer to the bottom. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/velocityU_nocolumn}
    \caption{time history of streamwise velocity U for case without a column}
    \label{fig:velocityU_nocolumn}
\end{figure}

>>>>

In all cases below, boundary conditions are all set to reflection wall. 
\section{Dam Break}\label{Sec:Zero}
The initial condition for this and the following cases is given by
\eqm
h_0(x,y)=& 
\begin{cases}
0.25 & x<5.9 \\
0.02 & \text{otherwise}
\end{cases}\\
u_0(x,y) =& 0
\enm
In this comparison we will include results from OpenFOAM, an open source CFD software modeling air and water using the Navier-Stokes equations with turbulence model.
Figure \ref{fig:waveheight_nocolumn} shows the time history of the wave height measured at the center location where the column will be mounted. 
Result from GeoClaw agree quite well in general(Show zoom in plot). At around t=3.8, GeoClaw accurately predicted the arrival of the shock. 
GeoClaw overestimates the peak water level a little, while OpenFOAM, gives a better value.
After a later time, the wave gets reflected at the right wall of the tank, which can be seen by the second jump in wave height. 
GeoClaw also predicts the arrival time of this peak quite well by overestimating the peak value by a small amount.
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/waveheight_nocolumn}
    \caption{time history of wave height for case without a column}
    \label{fig:waveheight_nocolumn}
\end{figure}

Figure \ref{fig:velocityU_nocolumn} gives the time history of the streamwise velocity $u$ from GeoClaw and experiment. 
Note that this velocity $u$ in both GeoClaw and experiment are depth-averaged. 
GeoClaw accurately predicted the time of the velocity peak as well as the value of the peak. 
After the peak arrived, GeoClaw overestimated the value of velocity.
The reason why GeoClaw gives a higher velocity may be attributed to its depth-averaged property: Water at all depth are propagating with the same speed. In the experiment, the velocity is getting smaller the closer we get to the bottom. 
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{./plots/velocityU_nocolumn}
    \caption{time history of streamwise velocity U for case without a column}
    \label{fig:velocityU_nocolumn}
\end{figure}
